---
title: "Boston data test"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Import
```{r}
library(MASS) # 資料來源
library(car) # VIF函數來源
#mydata <- read.table(, header = TRUE, na.strings = "?")
#mydata <- read.csv(, header = TRUE, na.strings = "?")
```
# Tidy
```{r}
my_Boston <- na.omit(Boston) # 移除含有空值的資料
```
## Begin Understand
# Transform
```{r}
#summary(Boston)
```

crim : per capita crime rate by town.  
zn : proportion of residential land zoned for lots over 25,000 sq.ft.  
indus : proportion of non-retail business acres per town  
chas : Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).  
nox : nitrogen oxides concentration (parts per 10 million).  
rm : average number of rooms per dwelling.  
age : proportion of owner-occupied units built prior to 1940.  
dis : weighted mean of distances to five Boston employment centres.  
rad : index of accessibility to radial highways.  
tax : full-value property-tax rate per \$10,000.  
ptratio : pupil-teacher ratio by town.  
black : 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.  
lstat : lower status of the population (percent).  
**medv : median value of owner-occupied homes in \$1000s.**
```{r}
#plot(rm, lstat)
#hist(lstat, col=2, breaks = 15)
#pairs(my_Boston)
#pairs(~ + rm + crim + lstat)
#cor(my_Boston)
```

# Visualize
## interactive terms?
## polynomial terms?
Adjust this on preditors to make plot (residuals plot) a horizontal red line.  
Adjust this on response to make residuals plot a uniform shape.

## outliers? High leverage point?
Residual plot tells which row

## colinear?
check if vif > 5

# Model
```{r}
attach(my_Boston)
lm.fit = lm(medv ~ ., data = my_Boston)
summary(lm.fit)
vif(lm.fit)
lm.fit = lm(medv ~ . -age -indus - tax, data = my_Boston)
summary(lm.fit)
plot(lm.fit)
lm.fit = lm(medv ~ . - tax - indus - age , data = my_Boston[-c(369, 372, 373), ])
summary(lm.fit)
plot(lm.fit)
lm.fit3 = lm(medv ~ . - tax - indus - age + I(rm^2), data = my_Boston[-c(372, 373, 369), ])
summary(lm.fit3)
plot(lm.fit3)
anova(lm.fit, lm.fit3)
```

## End Understand

# Communicate

```{r}
lm.fit4 = lm(medv ~ . - tax - black - zn - rad - chas - indus - age + I(rm^2) + rm:lstat, data = my_Boston[-c(365, 370, 371, 372, 373, 369), ])
summary(lm.fit4)
plot(lm.fit4)
# wierd data
my_Boston[c(365, 370, 371, 372, 373, 369), ]
```

